%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.5\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Felipe}}}}} % First name
	
	\colorbox{black}{{\large\textcolor{white}{\textbf{\MakeUppercase{dos Santos Neves}}}}} % Last name
	
	\vspace{6pt}
	
	{\huge Embedded Software Developer} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.5\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	%\icon{Globe}{12}{\href{https://alyx.vance.me}{alyx.vance.me}}\\
	%\icon{Github}{12}{\href{https://github.com/alyxvance}{github.com/alyxvance}}\\
	%\icon{Twitter}{12}{\href{https://twitter.com/@alyxvance}{@alyxvance}}\\
	\icon{MapMarker}{12}{Curitiba/PR - Brazil}\\
	\icon{Phone}{12}{031 06010334654}\\
	\icon{At}{12}{\href{mailto:feupos@hotmail.com}{feupos@hotmail.com}}\\	
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{Who Am I?}

\begin{minipage}[t]{0.4\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	I am a 28 year old software developer from Brazil. Currently I live in the Netherlands with my wife.
    I moved to the Netherlands for a job opportuny after finishing my Master's degree, to work with projects in the semiconductor manufacturing field. My main intersts in the software development field are working and improving my knowledge with modern C++ as well as learning new programming languages (such as Rust).
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.5\textwidth} % 50% of the page for the skills bar chart
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\begin{barchart}{5.5}
		\baritem{C++(11/14)}{100}
        \baritem{C++(17/20)}{80}
		\baritem{Python}{70}
  	\baritem{C}{60}
		%\baritem{UML}{50}
		\baritem{LaTeX}{40}
	\end{barchart}
\end{minipage}

%\begin{center}
%	\bubbles{4/Linux, 5/Git, 4/Agile, 4/JIRA}
%\end{center}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
		{2021 -- Current}
		{Software Engineer}
		{ASML (through ICT Group}
		{Working in outsourced projects for ASML through ICT Group. Development of Calibration, Performance and Diagnostics Software for lithografy machines, with the use of proprietary Python frameworks, as well as C/C++ code for lower level interfaces and drivers. Worked as a developer in a 5 people team within a large organization the use of the SAFe methodlogy.}
	\entry
		{2018 -- 2021}
		{Embedded Software Developer}
		{Alta Rail Technology}
		{Development of software in C, C++ and Python for embedded systems using On-Time RTOS and
		Linux for railway applications. Involved with development of core system applications such
		as the safety navigation module (MISRA C compliant), and communications protocols for hybrid
		networks for efficient communications on low speed networks as well as GUI for On-Time RTOS
		and performing code review using Gerrit and troubleshooting/debugging. Also writing functional
		specification and risk analysis documents for products.}
	\entry
		{2017 -- 2018\\\footnotesize{part time}}
		{Software Development Intern}
		{Alta Rail Technology}
		{Development of software in C, C++ and Python for embedded systems using On-Time RTOS and 
		Linux for railway applications.}
	\entry
		{2016 -- 2017\\\footnotesize{part time}}
		{Quality Assurance Intern}
		{Alta Rail Technology}
		{Inspect, test and measure materials and equipments to ensure that they meet production standards.}
	\entry
		{2012 -- 2013\\\footnotesize{part time}}
		{Technical Assitance Intern}
		{NHS Electronic Systems}
		{Performed electronic hardware maintenance in UPS systems.}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{2019 -- 2021}
		{Master's Degree in Applied Computing (Computer Science)}
		{Universidade Tecnológica Federal do Paraná - Brazil}
		{Development of a C++ framework for the Notification Oriented Paradigm with generic programming and thread safety}
	\entry
		{2012 -- 2018}
		{Bachelor's Degree in Electronic Engineering}
		{Universidade Tecnológica Federal do Paraná - Brazil}
		{}
	\entry
		{2015 -- 2016}
		{Science Without Borders Program}
		{Shibaura Institute of Technology - Japan}
		{Member of Brain-Computer interfaces research laboratory at the institute}
	\entry
		{2009 -- 2012}
		{Technical Degree in Electronics}
		{Universidade Tecnológica Federal do Paraná - Brazil}
		{}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Languages}
	
	\textbf{Portuguese} - native\\
	\textbf{English} - fluent\\\\
    \textbf{Dutch} - basic
	\textbf{Japanese} - basic
\end{minipage}
\hfill
\begin{minipage}[t]{0.7\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Hobbies \& Others}

	I am a huge cinema geek, going to the movies whenever I can, and I am also really into all
	types of games, being it computer games, card games, board games. 
    I am a shy but very social person, and I love hosting game nights at my house.
\end{minipage}


%----------------------------------------------------------------------------------------

\end{document}
